Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-12 Appendix.tex
appendix

\documentclass[main.tex]{subfiles}
\begin{document}

\chapter*{List of Symbols}

% Vector Spaces and Related Concepts
\noindent
\textbf{Vector Spaces and Related Concepts}\\
\begin{tabularx}{\textwidth}{cXr}
\toprule
Symbol & Description & First Appearance (Page) \\ 
\midrule
\( \mathbb{N} \) & set of natural numbers \( j \) & \pageref{sym:natural} \\
\( R^n \) & n-dimensional space of real numbers & \pageref{sym:Rn} \\
\( \Omega \) & subset of \( R^n \), usually representing a body/reference configuration & \pageref{sym:Omega} \\
\( \partial \Omega \) & the boundary of $\Omega$ & \pageref{sym:boundaryOmega} \\
\( \bar{\Omega} \) & the boundary of $\Omega$ & \pageref{sym:baromega} \\
\( C^n \) & set of n-times continuously differentiable functions & \pageref{sym:Cn} \\
\( C^\infty \) & space of smooth functions & \pageref{sym:Cinfty} \\
\( C^\infty_0 \) & space of smooth functions with compact support & \pageref{sym:Cinftyzero} \\
\( L^n \) & space of n-power Lebesgue integrable functions & \pageref{sym:Ln} \\
\( H^n \) & space of functions with weak derivatives up to order n (n'th dimensional Sobolev space) & \pageref{sym:Hn} \\
\( X \) & global space & \pageref{sym:Xspace} \\
\( V \) & inertia space & \pageref{sym:Wspace} \\
\( W \) & energy space & \pageref{sym:Vspace} \\
\( T(\Omega) \) & test function space on \( \Omega \) & \pageref{sym:TOmega} \\
\( S^h \) & finite dimensional subspace & \pageref{sym:Sh1} \\
\( \mathcal{P}_j \) & set of all polynomials of degree at most \( j \) & \pageref{sym:poly} \\
\( E_n \) & space spanned by the orthonormal basis vectors $e_i$ & \pageref{sym:En} \\

@@

>>>>

\documentclass[main.tex]{subfiles}
\begin{document}
\chapter*{Appendix}
\addcontentsline{toc}{chapter}{Appendix}

\section*{List of symbols}
\addcontentsline{toc}{section}{List of symbols}

This list of symbols contain some of the most used symbols in this dissertation. The symbols are grouped into three categories: Vector Spaces and Related Concepts, Mathematical Measures and Operations, and Physical Quantities and Parameters. The first appearance of each symbol is also listed.

Other symbols that are section specific or that are contextually evident might not be in this list.

% Vector Spaces and Related Concepts
\noindent
\textbf{Vector Spaces and Related Co
ncepts}\\
\begin{tabularx}{\textwidth}{cXr}
\toprule
Symbol & Description & First Appearance (Page) \\ 
\midrule
\( \mathbb{N} \) & set of natural numbers \( j \) & \pageref{sym:natural} \\
\( R^n \) & n-dimensional space of real numbers & \pageref{sym:Rn} \\
\( \Omega \) & subset of \( R^n \), usually representing a body/reference configuration & \pageref{sym:Omega} \\
\( \partial \Omega \) & the boundary of $\Omega$ & \pageref{sym:boundaryOmega} \\
\( \bar{\Omega} \) & the boundary of $\Omega$ & \pageref{sym:baromega} \\
\( C^n \) & set of n-times continuously differentiable functions & \pageref{sym:Cn} \\
\( C^\infty \) & space of smooth functions & \pageref{sym:Cinfty} \\
\( C^\infty_0 \) & space of smooth functions with compact support & \pageref{sym:Cinftyzero} \\
\( L^n \) & space of n-power Lebesgue integrable functions & \pageref{sym:Ln} \\
\( H^n \) & space of functions with weak derivatives up to order n (n'th dimensional Sobolev space) & \pageref{sym:Hn} \\
\( X \) & global space & \pageref{sym:Xspace} \\
\( V \) & inertia space & \pageref{sym:Wspace} \\
\( W \) & energy space & \pageref{sym:Vspace} \\
\( T(\Omega) \) & test function space on \( \Omega \) & \pageref{sym:TOmega} \\
\( S^h \) & finite dimensional subspace & \pageref{sym:Sh1} \\
\( \mathcal{P}_j \) & set of all polynomials of degree at most \( j \) & \pageref{sym:poly} \\
\( E_n \) & space spanned by the orthonormal basis vectors $e_i$ & \pageref{sym:En} \\

@@

\section*{Sobolev spaces}
\addcontentsline{toc}{section}{Sobolev spaces}

\subsection*{The Space $L^2$}
Consider a measurable space $X$. The set of square integrable functions is called the $L^2$ space.\\

The inner product of $L^2$ is defined as 
\begin{eqnarray*}
	(f,g) = \int_X fg \ \ \ \ \textrm { for } f,g \in L2.
\end{eqnarray*}
The norm can be defined as $||f|| = (f,f)^{\frac{1}{2}}$ for each $f \in L^2(X)$. For reference, see \cite{Rud53}.

\subsection*{The Space \( L^p \)}
Consider a measurable space \( X \). For a real number \( p \geq 1 \), the set of \( p \)-integrable functions is called the \( L^p \) space. A function \( f \) belongs to \( L^p(X) \) if the \( p \)-th power of its absolute value is Lebesgue integrable, that is, if
\begin{eqnarray*}
    \int_X |f|^p < \infty.
\end{eqnarray*}

The \( L^p \) norm (or \( p \)-norm) is defined as
\begin{eqnarray*}
    ||f||_p = \left( \int_X |f|^p \right)^{\frac{1}{p}}
\end{eqnarray*}
for each \( f \in L^p(X) \).

\subsection*{Continuous function spaces}
$C^m(a,b)$ is the space of functions with continuous derivatives up to order $m$ over the open interval (a,b).

$C^m[a,b]$ is the space of functions in $C^m(a,b)$, with existing right derivatives at $a$ and existing left derivatives at $b$, up to order m.

$C_0^m(a,b)$ contains all functions $f$ in $C^m[a,b]$ with the property that there exists numbers $a < \alpha < \beta < b$ such that $f$ is zero on $[a,\alpha] \cup [\beta, b]$. This property is called compact support.

$C^\infty(a,b)$ contains all functions in $C^m(a,b)$ for all $m$.

$C^\infty[a,b]$ contains all functions in $C^m[a,b]$ for all $m$.

$C_0^\infty(a,b)$ contains all functions in $C_0^m(a,b)$ for all $m$.

\subsection*{First order weak derivative}
Suppose $u \in L^2(a,b)$ and there exist a $v \in L^2(a,b)$ such that
\begin{eqnarray*}
	(u,\phi') = -(v,\phi) \ \textrm{ for each } \phi \in C^{\infty}_0(a,b)
\end{eqnarray*}
then $v$ is called the first order weak derivative of $u$ and is denoted by $Du$.

\subsection*{Higher order weak derivative}
Suppose $u \in L^2(a,b)$ and there exist a $v \in L^2(a,b)$ such that
\begin{eqnarray*}
	(u,\phi^{(m)}) = (-1)^{(m)}(v,\phi) \ \textrm{ for each } \phi \in C^{\infty}_0(a,b)
\end{eqnarray*}
then $v$ is called the m'th order weak derivative of $u$ and is denoted by $D^{(m)}u$.

\subsection*{Sobolev spaces}

$W^n$ is the space of functions with weak derivatives up to order $n$. There are also special notation $W^{n,p}$ that indicates that the functions are P-intergrable.

$H^n$ is the space of functions with weak derivatives up to order $n$ and the functions are square integrable. (i.e. $H^n = W^{n,2}$)

### 2023-11-12 files/Chapter3/dynamicconvergence.tex
appendix

\section{Convergence of the Galerkin approximation}\label{sec:convergence-of-the-galerkin-approximation}
In the article \cite{BV13}, the authors investigate the convergence of the
Galerkin approximation for second order hyperbolic type problems. The article
\cite{BV18} extends the work of \cite{BV13} by including general damping and
damping at the endpoints. For the models in Chapter 1, \cite{BV13} is
sufficient while \cite{BV18} provides more insight and improved notation.

>>>>

\section{Convergence of the Galerkin approximation}\label{sec:convergence-of-the-galerkin-approximation}
In the article \cite{BV13}, the authors investigate the convergence of the
Galerkin approximation for second order hyperbolic type problems. The article
\cite{BSV17} extends the work of \cite{BV13} by including general damping and
damping at the endpoints. For the models in Chapter 1, \cite{BV13} is
sufficient while \cite{BSV17} provides more insight and improved notation.

### 2023-11-12 files/Overview.tex
appendix

The first section is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model. The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis). The two-dimensional model is more complex and there are eigenvalues that are not shared between the models. The authors use the mode shapes to match up the eigenvalues. The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues. The authors also consider different shapes of beams, from a short fat beam to a long slender beam. The results show that the models compare very well, even for a short and fat beam. As the beam gets more slender, the comparison improves. In this section some of the results of the article are discussed and replicated.

But in real-world applications, a beam is a three-dimensional model. Therefore it would be more suited to use a three-dimensional model to investigate the validity of the Timoshenko beam theory. This is mentioned by the authors of \cite{LVV09}. Their suggestion is to use the two-dimensional model as an intermediate step, to avoid complexities. Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference. Again the results so that the comparison relies on the shape of the beams. The two-dimensional model compares well to the three-dimensional beam if the beam is not very wide.

If the width of the beam is very large, the use of a beam model can be questioned. A plate model might be more suited. Therefore the last section of this chapter investigates the validity of the Reissner-Mindlin plate model. The Reissner-Mindlin plate model is compared to a three-dimensional plate model. The results show that the Reissner-Mindlin plate model compares well to the three-dimensional plate model. This is also true for a wide plate.

Overall the models compare very well, as long as the shape of the model is realistic.

@@

The in \cite{BV13} the authors prove that this error can be made arbitrarily small by choosing a sufficiently small $h$, such that $u^h \rightarrow u$ as $h \rightarrow 0$. \cite{BV18} extends \cite{BV13} to include damping.\\

>>>>

The first section is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model. The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis). The two-dimensional model is more complex and there are eigenvalues that are not shared between the models. The authors use the mode shapes to match up the eigenvalues. The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues. The authors also consider different shapes of beams, from a short thick beam to a long slender beam. The results show that the models compare very well, even for a short and thick beam. As the beam gets more slender, the comparison improves. In this section some of the results of the article are discussed and replicated.

But in real-world applications, a beam is a three-dimensional model. Therefore it should be more realistic to use a three-dimensional model to investigate the validity of the Timoshenko beam theory. This is mentioned by the authors of \cite{LVV09}. Their suggestion is to use the two-dimensional model as an intermediate step, to avoid complexities. Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference. Again the results so that the comparison relies on the shape of the beams. The two-dimensional model compares well to the three-dimensional beam if the beam is not wide.

If the width of the beam is very large, the use of a beam model can be questioned. A plate model might be more suited. Therefore the last section of this chapter investigates the validity of the Reissner-Mindlin plate model. The Reissner-Mindlin plate model is compared to a three-dimensional plate model. The results show that the Reissner-Mindlin plate model compares well to the three-dimensional plate model.

@@

The in \cite{BV13} the authors prove that this error can be made arbitrarily small by choosing a sufficiently small $h$, such that $u^h \rightarrow u$ as $h \rightarrow 0$. \cite{BSV17} extends \cite{BV13} to include damping.\\
